Main manuscript

### 2021-10-26 Manuscript/Manuscript.tex
small typo
fixed locazation problem that was misplacing commas around quot marks

{[}1{]} 8

@@

We built an R (R Core Team 2020) based framework to simplify two aspects
of systematic reviews: record acquisition and classification. The
framework comprises several modules that communicate through
intermediate outputs stored in standard formats, which make it possible
for users to extend the framework or easily integrate it with other
tools in their pipeline. See Supplemental Material S1 for an in-depth
description of the framework and how to use it.\\
The tasks carried out by the framework are grouped into ``sessions,''
i.e., a set of actions that starts from a search query to obtain a set
of scientific citation data (records), which are then labelled as
relevant (``positive'' in the rest of the text) or not (``negative'')
for the topic of interest (Fig. 1). The framework can generate a new
query from this labelled set and perform a new session to find records
possibly missed by the first query.\\
The researcher initiates the process with a starting query derived by
domain knowledge from which she expects a high relevant/non-relevant
record ratio.\\
Follows a description of the framework's components.\\

@@

We built a set of tools to let users automatically search and download
citation data from three major scientific databases (``sources''):
Pubmed (\url{https://pubmed.ncbi.nlm.nih.gov/}), Web Of Science (WOS,
\url{https://apps.webofknowledge.com/}) and the Institute of Electrical
and Electronics Engineers (IEEE,
\url{https://ieeexplore.ieee.org/Xplore/home.jsp}). The framework takes
care of authorization management for non-open databases like WOS and
IEEE. It is also possible to download and import records in the
framework manually; this is particularly useful to acquire records from
the SCOPUS
(\url{https://www.scopus.com/search/form.uri?display=basic\#basic}) and
EMBASE databases
(\url{https://www.embase.com/\#advancedSearch/default}), for which a
comprehensive API interface was not easy to build. An extra manual
search was necessary also for Pubmed, since the API and the web
interface have different rule expansion algorithms and return slightly
different results ({``NCBI Insights : Updated Pubmed e-Utilities Coming
in April 2022!''} n.d.). A short guide on how to set up the framework
for each supported database is available in Supplemental Material S3.\\
The acquired records are merged into a single database, resolving
duplicates and different formatting between sources. The records are
ordered according to the frequency of the positive query terms (e.g.,
not preceded by a \(NOT\) modifier) in the title and abstract (``simple
query ordering'').\\
The researcher is then asked to label a number of records to create the
``initial training set'' needed to start the automatic classification.
We suggest manually labelling the first 250 records (see
``hyperparameter optimization'' later). The simple query ordering
increases the positivity rate in the initial training set (Wallace,
Small, et al. 2010), which provide higher sensitivity during automatic
classification (Chawla, Japkowicz, and Kotcz 2004).

@@

All other records are labelled as ``uncertain.''

@@

\caption{\label{tab:session 1}\textbf{Table 1}. Distribution of retrieved records by source and session. For each source it is reported the number of records, percentage over the session total (after removing duplicates)' and, number or records specific for a source as absolute value and as percentage over the source total. SAll session shows records after joining and deduplication of the Session 1 and Session 2 dataset.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llrlrl}
\toprule
Session & Source & Records & \% over total & Source specific records & \% over source total\\
\midrule
\cellcolor{gray!6}{Session1} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{17755} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
 & Embase & 12719 & 71.6\% & 6683 & 52.5\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{9546} & \cellcolor{gray!6}{53.8\%} & \cellcolor{gray!6}{3457} & \cellcolor{gray!6}{36.2\%}\\
 & Scopus & 3175 & 17.9\% & 298 & 9.39\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{2100} & \cellcolor{gray!6}{11.8\%} & \cellcolor{gray!6}{473} & \cellcolor{gray!6}{22.5\%}\\
\addlinespace
 & IEEE & 60 & 0.34\% & 29 & 48.3\%\\
\cellcolor{gray!6}{Session2} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{82579} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
 & Embase & 48396 & 58.6\% & 40826 & 84.4\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{28811} & \cellcolor{gray!6}{34.9\%} & \cellcolor{gray!6}{18021} & \cellcolor{gray!6}{62.5\%}\\
 & Scopus & 17070 & 20.7\% & 4908 & 28.8\%\\
\addlinespace
\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{12956} & \cellcolor{gray!6}{15.7\%} & \cellcolor{gray!6}{2817} & \cellcolor{gray!6}{21.7\%}\\
 & IEEE & 61 & 0.074\% & 22 & 36.1\%\\
\cellcolor{gray!6}{All Sessions} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{98371} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
 & Embase & 59604 & 60.6\% & 46942 & 78.8\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{37278} & \cellcolor{gray!6}{37.9\%} & \cellcolor{gray!6}{21371} & \cellcolor{gray!6}{57.3\%}\\
\addlinespace
 & Scopus & 19353 & 19.7\% & 5181 & 26.8\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{14367} & \cellcolor{gray!6}{14.6\%} & \cellcolor{gray!6}{3175} & \cellcolor{gray!6}{22.1\%}\\
 & IEEE & 108 & 0.11\% & 48 & 44.4\%\\
\bottomrule
\end{tabular}}
\end{table}

@@

One of the central innovations we introduced is the concept of
``uncertainty zone,'' whose implementation is possible thanks to the
Bayesian foundation of the classification model. This construct guides
the selection of the records to review, dynamically updating and
shrinking after every CR iteration, as more uncertain predictions are
evaluated (Supplemental Material S2 Fig. 1).\\
This approach overcomes the usual requirement of dataset-specific hard
thresholds in active machine learning, and also allows to review
multiple items at once between iterations (Laws and Schütze 2008; Miwa
et al. 2014; Zhu et al. 2010). The parameters our algorithm needs are
instead quite general and non task-specific, like the PPD intervals
based on which the uncertainty zone is built ,and the maximum number of
iterations with no positive matches after which a session is concluded;
the hyperparamer evaluation shows that the algorithm is robust against
variations in these parameters and we expect the default values to
preform well on most datasets.\\
Since researchers are asked to review both records with a positive
predicted label and those inside the uncertainty zone, this method can
be considered as a unifying synthesis of the ``certainty'' and
``uncertainty'' paradigms of active learning (Miwa et al. 2014).\\

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-abd2013review}{}%
Abd Elrahman, Shaza M, and Ajith Abraham. 2013. {``A Review of Class
Imbalance Problem.''} \emph{Journal of Network and Innovative Computing}
1 (2013): 332--40.

\leavevmode\hypertarget{ref-allen1999estimating}{}%
Allen, I Elaine, and Ingram Olkin. 1999. {``Estimating Time to Conduct a
Meta-Analysis from Number of Citations Retrieved.''} \emph{Jama} 282
(7): 634--35.

@@

\leavevmode\hypertarget{ref-ananiadou2009supporting}{}%
Ananiadou, Sophia, Brian Rea, Naoaki Okazaki, Rob Procter, and James
Thomas. 2009. {``Supporting Systematic Reviews Using Text Mining.''}
\emph{Social Science Computer Review} 27 (4): 509--23.

\leavevmode\hypertarget{ref-aviv2021publication}{}%
Aviv-Reuven, Shir, and Ariel Rosenfeld. 2021. {``Publication Patterns'
Changes Due to the COVID-19 Pandemic: A Longitudinal and Short-Term
Scientometric Analysis.''} \emph{Scientometrics}, 1--24.

\leavevmode\hypertarget{ref-babar2009systematic}{}%
Babar, Muhammad Ali, and He Zhang. 2009. {``Systematic Literature
Reviews in Software Engineering: Preliminary Results from Interviews
with Researchers.''} In \emph{2009 3rd International Symposium on
Empirical Software Engineering and Measurement}, 346--55. IEEE.

@@

\leavevmode\hypertarget{ref-bajpai2011search}{}%
Bajpai, Akhilesh, Sravanthi Davuluri, Haritha Haridas, Greta Kasliwal, H
Deepti, KS Sreelakshmi, Darshan Chandrashekar, et al. 2011. {``In Search
of the Right Literature Search Engine (s).''} \emph{Nature Precedings},
1--1.

\leavevmode\hypertarget{ref-bannach2019machine}{}%
Bannach-Brown, Alexandra, Piotr Przybyła, James Thomas, Andrew SC Rice,
Sophia Ananiadou, Jing Liao, and Malcolm Robert Macleod. 2019.
{``Machine Learning Algorithms for Systematic Review: Reducing Workload
in a Preclinical Review of Animal Studies and Reducing Human Screening
Error.''} \emph{Systematic Reviews} 8 (1): 1--12.

\leavevmode\hypertarget{ref-bastian2010seventy}{}%
Bastian, Hilda, Paul Glasziou, and Iain Chalmers. 2010. {``Seventy-Five
Trials and Eleven Systematic Reviews a Day: How Will We Ever Keep Up?''}
\emph{PLoS Medicine} 7 (9): e1000326.

\leavevmode\hypertarget{ref-batista2004study}{}%
Batista, Gustavo EAPA, Ronaldo C Prati, and Maria Carolina Monard. 2004.
{``A Study of the Behavior of Several Methods for Balancing Machine
Learning Training Data.''} \emph{ACM SIGKDD Explorations Newsletter} 6
(1): 20--29.

\leavevmode\hypertarget{ref-bekhuis2010towards}{}%
Bekhuis, Tanja, and Dina Demner-Fushman. 2010. {``Towards Automating the
Initial Screening Phase of a Systematic Review.''} \emph{MEDINFO 2010},
146--50.

\leavevmode\hypertarget{ref-bekhuis2012screening}{}%
---------. 2012. {``Screening Nonrandomized Studies for Medical
Systematic Reviews: A Comparative Study of Classifiers.''}
\emph{Artificial Intelligence in Medicine} 55 (3): 197--207.

\leavevmode\hypertarget{ref-beller2013systematic}{}%
Beller, Elaine M, Joyce Kee-Hsin Chen, Una Li-Hsiang Wang, and Paul P
Glasziou. 2013. {``Are Systematic Reviews up-to-Date at the Time of
Publication?''} \emph{Systematic Reviews} 2 (1): 1--6.

\leavevmode\hypertarget{ref-beller2018making}{}%
Beller, Elaine, Justin Clark, Guy Tsafnat, Clive Adams, Heinz Diehl,
Hans Lund, Mourad Ouzzani, et al. 2018. {``Making Progress with the
Automation of Systematic Reviews: Principles of the International
Collaboration for the Automation of Systematic Reviews (ICASR).''}
\emph{Systematic Reviews} 7 (1): 1--7.

\leavevmode\hypertarget{ref-bhatt2020machine}{}%
Bhatt, Umang, McKane Andrus, Adrian Weller, and Alice Xiang. 2020.
{``Machine Learning Explainability for External Stakeholders.''}
\emph{arXiv Preprint arXiv:2007.05408}.

\leavevmode\hypertarget{ref-bibal2021legal}{}%
Bibal, Adrien, Michael Lognoul, Alexandre De Streel, and Benoît Frénay.
2021. {``Legal Requirements on Explainability in Machine Learning.''}
\emph{Artificial Intelligence and Law} 29 (2): 149--69.

\leavevmode\hypertarget{ref-bibal2020impact}{}%
Bibal, Adrien, Michael Lognoul, Alexandre de Streel, and Benoît Frénay.
2020. {``Impact of Legal Requirements on Explainability in Machine
Learning.''} \emph{arXiv Preprint arXiv:2007.05479}.

\leavevmode\hypertarget{ref-blanco2019machine}{}%
Blanco-Justicia, Alberto, and Josep Domingo-Ferrer. 2019. {``Machine
Learning Explainability Through Comprehensible Decision Trees.''} In
\emph{International Cross-Domain Conference for Machine Learning and
Knowledge Extraction}, 15--26. Springer.

\leavevmode\hypertarget{ref-bollegala2015embedding}{}%
Bollegala, Danushka, Takanori Maehara, and Ken-ichi Kawarabayashi. 2015.
{``Embedding Semantic Relations into Word Representations.''} In
\emph{Twenty-Fourth International Joint Conference on Artificial
Intelligence}.

\leavevmode\hypertarget{ref-borah2017analysis}{}%
Borah, Rohit, Andrew W Brown, Patrice L Capers, and Kathryn A Kaiser.
2017. {``Analysis of the Time and Workers Needed to Conduct Systematic
Reviews of Medical Interventions Using Data from the PROSPERO
Registry.''} \emph{BMJ Open} 7 (2): e012545.

\leavevmode\hypertarget{ref-bornmann2015growth}{}%
Bornmann, Lutz, and Rüdiger Mutz. 2015. {``Growth Rates of Modern
Science: A Bibliometric Analysis Based on the Number of Publications and
Cited References.''} \emph{Journal of the Association for Information
Science and Technology} 66 (11): 2215--22.

\leavevmode\hypertarget{ref-breiman1996bagging}{}%
Breiman, Leo. 1996. {``Bagging Predictors.''} \emph{Machine Learning} 24
(2): 123--40.

\leavevmode\hypertarget{ref-burkart2021survey}{}%
Burkart, Nadia, and Marco F Huber. 2021. {``A Survey on the
Explainability of Supervised Machine Learning.''} \emph{Journal of
Artificial Intelligence Research} 70: 245--317.

\leavevmode\hypertarget{ref-chae1993presenting}{}%
Chae, Kyung-Chul. 1993. {``Presenting the Negative Hypergeometric
Distribution to the Introductory Statistics Courses.''}
\emph{International Journal of Mathematical Education in Science and
Technology} 24 (4): 523--26.

\leavevmode\hypertarget{ref-chawla2004special}{}%
Chawla, Nitesh V, Nathalie Japkowicz, and Aleksander Kotcz. 2004.
{``Special Issue on Learning from Imbalanced Data Sets.''} \emph{ACM
SIGKDD Explorations Newsletter} 6 (1): 1--6.

\leavevmode\hypertarget{ref-chen2018approximate}{}%
Chen, Chao, Xiao Lin, and Gabriel Terejanu. 2018. {``An Approximate
Bayesian Long Short-Term Memory Algorithm for Outlier Detection.''} In
\emph{2018 24th International Conference on Pattern Recognition (ICPR)},
201--6. IEEE.

\leavevmode\hypertarget{ref-chen2016short}{}%
Chen, Qiuxing, Lixiu Yao, and Jie Yang. 2016. {``Short Text
Classification Based on LDA Topic Model.''} In \emph{2016 International
Conference on Audio, Language and Image Processing (ICALIP)}, 749--53.
IEEE.

\leavevmode\hypertarget{ref-chen2015gaussian}{}%
Chen, Sih-Huei, Yuan-Shan Lee, Tzu-Chiang Tai, and Jia-Ching Wang. 2015.
{``Gaussian Process Based Text Categorization for Healthy
Information.''} In \emph{2015 International Conference on Orange
Technologies (ICOT)}, 30--33.
\url{https://doi.org/10.1109/ICOT.2015.7498487}.

\leavevmode\hypertarget{ref-cheng2019document}{}%
Cheng, Y, Z Ye, M Wang, and Q Zhang. 2019. {``Document Classification
Based on Convolutional Neural Network and Hierarchical Attention
Network.''} \emph{Neural Network World} 29 (2): 83--98.

\leavevmode\hypertarget{ref-chipman2010bart}{}%
Chipman, Hugh A, Edward I George, Robert E McCulloch, and others. 2010.
{``BART: Bayesian Additive Regression Trees.''} \emph{The Annals of
Applied Statistics} 4 (1): 266--98.

\leavevmode\hypertarget{ref-claesen2015hyperparameter}{}%
Claesen, Marc, and Bart De Moor. 2015. {``Hyperparameter Search in
Machine Learning.''} \emph{arXiv Preprint arXiv:1502.02127}.

\leavevmode\hypertarget{ref-cohen2010evidence}{}%
Cohen, Aaron M, Clive E Adams, John M Davis, Clement Yu, Philip S Yu,
Weiyi Meng, Lorna Duggan, Marian McDonagh, and Neil R Smalheiser. 2010.
{``Evidence-Based Medicine, the Essential Role of Systematic Reviews,
and the Need for Automated Text Mining Tools.''} In \emph{Proceedings of
the 1st ACM International Health Informatics Symposium}, 376--80.

\leavevmode\hypertarget{ref-cohen2006reducing}{}%
Cohen, Aaron M, William R Hersh, Kim Peterson, and Po-Yin Yen. 2006.
{``Reducing Workload in Systematic Review Preparation Using Automated
Citation Classification.''} \emph{Journal of the American Medical
Informatics Association} 13 (2): 206--19.

\leavevmode\hypertarget{ref-cohen2008getting}{}%
Cohen, K Bretonnel, and Lawrence Hunter. 2008. {``Getting Started in
Text Mining.''} \emph{PLoS Computational Biology} 4 (1): e20.

\leavevmode\hypertarget{ref-dietterich2000ensemble}{}%
Dietterich, Thomas G. 2000. {``Ensemble Methods in Machine Learning.''}
In \emph{International Workshop on Multiple Classifier Systems}, 1--15.
Springer.

>>>>

@@

We built an R (R Core Team 2020) based framework to simplify two aspects
of systematic reviews: record acquisition and classification. The
framework comprises several modules that communicate through
intermediate outputs stored in standard formats, which make it possible
for users to extend the framework or easily integrate it with other
tools in their pipeline. See Supplemental Material S1 for an in-depth
description of the framework and how to use it.\\
The tasks carried out by the framework are grouped into ``sessions'',
i.e., a set of actions that starts from a search query to obtain a set
of scientific citation data (records), which are then labelled as
relevant (``positive'' in the rest of the text) or not (``negative'')
for the topic of interest (Fig. 1). The framework can generate a new
query from this labelled set and perform a new session to find records
possibly missed by the first query.\\
The researcher initiates the process with a starting query derived by
domain knowledge from which she expects a high relevant/non-relevant
record ratio.\\
Follows a description of the framework's components.\\

@@

We built a set of tools to let users automatically search and download
citation data from three major scientific databases (``sources''):
Pubmed (\url{https://pubmed.ncbi.nlm.nih.gov/}), Web Of Science (WOS,
\url{https://apps.webofknowledge.com/}) and the Institute of Electrical
and Electronics Engineers (IEEE,
\url{https://ieeexplore.ieee.org/Xplore/home.jsp}). The framework takes
care of authorization management for non-open databases like WOS and
IEEE. It is also possible to download and import records in the
framework manually; this is particularly useful to acquire records from
the SCOPUS
(\url{https://www.scopus.com/search/form.uri?display=basic\#basic}) and
EMBASE databases
(\url{https://www.embase.com/\#advancedSearch/default}), for which a
comprehensive API interface was not easy to build. An extra manual
search was necessary also for Pubmed, since the API and the web
interface have different rule expansion algorithms and return slightly
different results ({`NCBI Insights : Updated Pubmed e-Utilities Coming
in April 2022!'} n.d.). A short guide on how to set up the framework for
each supported database is available in Supplemental Material S3.\\
The acquired records are merged into a single database, resolving
duplicates and different formatting between sources. The records are
ordered according to the frequency of the positive query terms (e.g.,
not preceded by a \(NOT\) modifier) in the title and abstract (``simple
query ordering'').\\
The researcher is then asked to label a number of records to create the
``initial training set'' needed to start the automatic classification.
We suggest manually labelling the first 250 records (see
``hyperparameter optimization'' later). The simple query ordering
increases the positivity rate in the initial training set (Wallace,
Small, et al. 2010), which provide higher sensitivity during automatic
classification (Chawla, Japkowicz, and Kotcz 2004).

@@

All other records are labelled as ``uncertain''.

@@

\caption{\label{tab:session 1}\textbf{Table 1}. Distribution of retrieved records by source and session. For each source it is reported the number of records, percentage over the session total (after removing duplicates)' and, number or records specific for a source as absolute value and as percentage over the source total. All session shows records after joining and deduplication of the Session 1 and Session 2 dataset.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llrlrl}
\toprule
Session & Source & Records & \% over total & Source specific records & \% over source total\\
\midrule
\cellcolor{gray!6}{Session1} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{17755} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
 & Embase & 12719 & 71.6\% & 6683 & 52.5\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{9546} & \cellcolor{gray!6}{53.8\%} & \cellcolor{gray!6}{3457} & \cellcolor{gray!6}{36.2\%}\\
 & Scopus & 3175 & 17.9\% & 298 & 9.39\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{2100} & \cellcolor{gray!6}{11.8\%} & \cellcolor{gray!6}{473} & \cellcolor{gray!6}{22.5\%}\\
\addlinespace
 & IEEE & 60 & 0.34\% & 29 & 48.3\%\\
\cellcolor{gray!6}{Session2} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{82579} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
 & Embase & 48396 & 58.6\% & 40826 & 84.4\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{28811} & \cellcolor{gray!6}{34.9\%} & \cellcolor{gray!6}{18021} & \cellcolor{gray!6}{62.5\%}\\
 & Scopus & 17070 & 20.7\% & 4908 & 28.8\%\\
\addlinespace
\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{12956} & \cellcolor{gray!6}{15.7\%} & \cellcolor{gray!6}{2817} & \cellcolor{gray!6}{21.7\%}\\
 & IEEE & 61 & 0.074\% & 22 & 36.1\%\\
\cellcolor{gray!6}{All Sessions} & \cellcolor{gray!6}{Total} & \cellcolor{gray!6}{98371} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{}\\
 & Embase & 59604 & 60.6\% & 46942 & 78.8\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Pubmed} & \cellcolor{gray!6}{37278} & \cellcolor{gray!6}{37.9\%} & \cellcolor{gray!6}{21371} & \cellcolor{gray!6}{57.3\%}\\
\addlinespace
 & Scopus & 19353 & 19.7\% & 5181 & 26.8\%\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{WOS} & \cellcolor{gray!6}{14367} & \cellcolor{gray!6}{14.6\%} & \cellcolor{gray!6}{3175} & \cellcolor{gray!6}{22.1\%}\\
 & IEEE & 108 & 0.11\% & 48 & 44.4\%\\
\bottomrule
\end{tabular}}
\end{table}

@@

One of the central innovations we introduced is the concept of
``uncertainty zone'', whose implementation is possible thanks to the
Bayesian foundation of the classification model. This construct guides
the selection of the records to review, dynamically updating and
shrinking after every CR iteration, as more uncertain predictions are
evaluated (Supplemental Material S2 Fig. 1).\\
This approach overcomes the usual requirement of dataset-specific hard
thresholds in active machine learning, and also allows to review
multiple items at once between iterations (Laws and Schütze 2008; Miwa
et al. 2014; Zhu et al. 2010). The parameters our algorithm needs are
instead quite general and non task-specific, like the PPD intervals
based on which the uncertainty zone is built ,and the maximum number of
iterations with no positive matches after which a session is concluded;
the hyperparamer evaluation shows that the algorithm is robust against
variations in these parameters and we expect the default values to
preform well on most datasets.\\
Since researchers are asked to review both records with a positive
predicted label and those inside the uncertainty zone, this method can
be considered as a unifying synthesis of the ``certainty'' and
``uncertainty'' paradigms of active learning (Miwa et al. 2014).\\

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-abd2013review}{}%
Abd Elrahman, Shaza M, and Ajith Abraham. 2013. {`A Review of Class
Imbalance Problem.'} \emph{Journal of Network and Innovative Computing}
1 (2013): 332--40.

\leavevmode\hypertarget{ref-allen1999estimating}{}%
Allen, I Elaine, and Ingram Olkin. 1999. {`Estimating Time to Conduct a
Meta-Analysis from Number of Citations Retrieved.'} \emph{Jama} 282 (7):
634--35.

@@

\leavevmode\hypertarget{ref-ananiadou2009supporting}{}%
Ananiadou, Sophia, Brian Rea, Naoaki Okazaki, Rob Procter, and James
Thomas. 2009. {`Supporting Systematic Reviews Using Text Mining.'}
\emph{Social Science Computer Review} 27 (4): 509--23.

\leavevmode\hypertarget{ref-aviv2021publication}{}%
Aviv-Reuven, Shir, and Ariel Rosenfeld. 2021. {`Publication Patterns'
Changes Due to the COVID-19 Pandemic: A Longitudinal and Short-Term
Scientometric Analysis.'} \emph{Scientometrics}, 1--24.

\leavevmode\hypertarget{ref-babar2009systematic}{}%
Babar, Muhammad Ali, and He Zhang. 2009. {`Systematic Literature Reviews
in Software Engineering: Preliminary Results from Interviews with
Researchers.'} In \emph{2009 3rd International Symposium on Empirical
Software Engineering and Measurement}, 346--55. IEEE.

@@

\leavevmode\hypertarget{ref-bajpai2011search}{}%
Bajpai, Akhilesh, Sravanthi Davuluri, Haritha Haridas, Greta Kasliwal, H
Deepti, KS Sreelakshmi, Darshan Chandrashekar, et al. 2011. {`In Search
of the Right Literature Search Engine (s).'} \emph{Nature Precedings},
1--1.

\leavevmode\hypertarget{ref-bannach2019machine}{}%
Bannach-Brown, Alexandra, Piotr Przybyła, James Thomas, Andrew SC Rice,
Sophia Ananiadou, Jing Liao, and Malcolm Robert Macleod. 2019. {`Machine
Learning Algorithms for Systematic Review: Reducing Workload in a
Preclinical Review of Animal Studies and Reducing Human Screening
Error.'} \emph{Systematic Reviews} 8 (1): 1--12.

\leavevmode\hypertarget{ref-bastian2010seventy}{}%
Bastian, Hilda, Paul Glasziou, and Iain Chalmers. 2010. {`Seventy-Five
Trials and Eleven Systematic Reviews a Day: How Will We Ever Keep Up?'}
\emph{PLoS Medicine} 7 (9): e1000326.

\leavevmode\hypertarget{ref-batista2004study}{}%
Batista, Gustavo EAPA, Ronaldo C Prati, and Maria Carolina Monard. 2004.
{`A Study of the Behavior of Several Methods for Balancing Machine
Learning Training Data.'} \emph{ACM SIGKDD Explorations Newsletter} 6
(1): 20--29.

\leavevmode\hypertarget{ref-bekhuis2010towards}{}%
Bekhuis, Tanja, and Dina Demner-Fushman. 2010. {`Towards Automating the
Initial Screening Phase of a Systematic Review.'} \emph{MEDINFO 2010},
146--50.

\leavevmode\hypertarget{ref-bekhuis2012screening}{}%
---------. 2012. {`Screening Nonrandomized Studies for Medical
Systematic Reviews: A Comparative Study of Classifiers.'}
\emph{Artificial Intelligence in Medicine} 55 (3): 197--207.

\leavevmode\hypertarget{ref-beller2013systematic}{}%
Beller, Elaine M, Joyce Kee-Hsin Chen, Una Li-Hsiang Wang, and Paul P
Glasziou. 2013. {`Are Systematic Reviews up-to-Date at the Time of
Publication?'} \emph{Systematic Reviews} 2 (1): 1--6.

\leavevmode\hypertarget{ref-beller2018making}{}%
Beller, Elaine, Justin Clark, Guy Tsafnat, Clive Adams, Heinz Diehl,
Hans Lund, Mourad Ouzzani, et al. 2018. {`Making Progress with the
Automation of Systematic Reviews: Principles of the International
Collaboration for the Automation of Systematic Reviews (ICASR).'}
\emph{Systematic Reviews} 7 (1): 1--7.

\leavevmode\hypertarget{ref-bhatt2020machine}{}%
Bhatt, Umang, McKane Andrus, Adrian Weller, and Alice Xiang. 2020.
{`Machine Learning Explainability for External Stakeholders.'}
\emph{arXiv Preprint arXiv:2007.05408}.

\leavevmode\hypertarget{ref-bibal2021legal}{}%
Bibal, Adrien, Michael Lognoul, Alexandre De Streel, and Benoît Frénay.
2021. {`Legal Requirements on Explainability in Machine Learning.'}
\emph{Artificial Intelligence and Law} 29 (2): 149--69.

\leavevmode\hypertarget{ref-bibal2020impact}{}%
Bibal, Adrien, Michael Lognoul, Alexandre de Streel, and Benoît Frénay.
2020. {`Impact of Legal Requirements on Explainability in Machine
Learning.'} \emph{arXiv Preprint arXiv:2007.05479}.

\leavevmode\hypertarget{ref-blanco2019machine}{}%
Blanco-Justicia, Alberto, and Josep Domingo-Ferrer. 2019. {`Machine
Learning Explainability Through Comprehensible Decision Trees.'} In
\emph{International Cross-Domain Conference for Machine Learning and
Knowledge Extraction}, 15--26. Springer.

\leavevmode\hypertarget{ref-bollegala2015embedding}{}%
Bollegala, Danushka, Takanori Maehara, and Ken-ichi Kawarabayashi. 2015.
{`Embedding Semantic Relations into Word Representations.'} In
\emph{Twenty-Fourth International Joint Conference on Artificial
Intelligence}.

\leavevmode\hypertarget{ref-borah2017analysis}{}%
Borah, Rohit, Andrew W Brown, Patrice L Capers, and Kathryn A Kaiser.
2017. {`Analysis of the Time and Workers Needed to Conduct Systematic
Reviews of Medical Interventions Using Data from the PROSPERO
Registry.'} \emph{BMJ Open} 7 (2): e012545.

\leavevmode\hypertarget{ref-bornmann2015growth}{}%
Bornmann, Lutz, and Rüdiger Mutz. 2015. {`Growth Rates of Modern
Science: A Bibliometric Analysis Based on the Number of Publications and
Cited References.'} \emph{Journal of the Association for Information
Science and Technology} 66 (11): 2215--22.

\leavevmode\hypertarget{ref-breiman1996bagging}{}%
Breiman, Leo. 1996. {`Bagging Predictors.'} \emph{Machine Learning} 24
(2): 123--40.

\leavevmode\hypertarget{ref-burkart2021survey}{}%
Burkart, Nadia, and Marco F Huber. 2021. {`A Survey on the
Explainability of Supervised Machine Learning.'} \emph{Journal of
Artificial Intelligence Research} 70: 245--317.

\leavevmode\hypertarget{ref-chae1993presenting}{}%
Chae, Kyung-Chul. 1993. {`Presenting the Negative Hypergeometric
Distribution to the Introductory Statistics Courses.'}
\emph{International Journal of Mathematical Education in Science and
Technology} 24 (4): 523--26.

\leavevmode\hypertarget{ref-chawla2004special}{}%
Chawla, Nitesh V, Nathalie Japkowicz, and Aleksander Kotcz. 2004.
{`Special Issue on Learning from Imbalanced Data Sets.'} \emph{ACM
SIGKDD Explorations Newsletter} 6 (1): 1--6.

\leavevmode\hypertarget{ref-chen2018approximate}{}%
Chen, Chao, Xiao Lin, and Gabriel Terejanu. 2018. {`An Approximate
Bayesian Long Short-Term Memory Algorithm for Outlier Detection.'} In
\emph{2018 24th International Conference on Pattern Recognition (ICPR)},
201--6. IEEE.

\leavevmode\hypertarget{ref-chen2016short}{}%
Chen, Qiuxing, Lixiu Yao, and Jie Yang. 2016. {`Short Text
Classification Based on LDA Topic Model.'} In \emph{2016 International
Conference on Audio, Language and Image Processing (ICALIP)}, 749--53.
IEEE.

\leavevmode\hypertarget{ref-chen2015gaussian}{}%
Chen, Sih-Huei, Yuan-Shan Lee, Tzu-Chiang Tai, and Jia-Ching Wang. 2015.
{`Gaussian Process Based Text Categorization for Healthy Information.'}
In \emph{2015 International Conference on Orange Technologies (ICOT)},
30--33. \url{https://doi.org/10.1109/ICOT.2015.7498487}.

\leavevmode\hypertarget{ref-cheng2019document}{}%
Cheng, Y, Z Ye, M Wang, and Q Zhang. 2019. {`Document Classification
Based on Convolutional Neural Network and Hierarchical Attention
Network.'} \emph{Neural Network World} 29 (2): 83--98.

\leavevmode\hypertarget{ref-chipman2010bart}{}%
Chipman, Hugh A, Edward I George, Robert E McCulloch, and others. 2010.
{`BART: Bayesian Additive Regression Trees.'} \emph{The Annals of
Applied Statistics} 4 (1): 266--98.

\leavevmode\hypertarget{ref-claesen2015hyperparameter}{}%
Claesen, Marc, and Bart De Moor. 2015. {`Hyperparameter Search in
Machine Learning.'} \emph{arXiv Preprint arXiv:1502.02127}.

\leavevmode\hypertarget{ref-cohen2010evidence}{}%
Cohen, Aaron M, Clive E Adams, John M Davis, Clement Yu, Philip S Yu,
Weiyi Meng, Lorna Duggan, Marian McDonagh, and Neil R Smalheiser. 2010.
{`Evidence-Based Medicine, the Essential Role of Systematic Reviews, and
the Need for Automated Text Mining Tools.'} In \emph{Proceedings of the
1st ACM International Health Informatics Symposium}, 376--80.

\leavevmode\hypertarget{ref-cohen2006reducing}{}%
Cohen, Aaron M, William R Hersh, Kim Peterson, and Po-Yin Yen. 2006.
{`Reducing Workload in Systematic Review Preparation Using Automated
Citation Classification.'} \emph{Journal of the American Medical
Informatics Association} 13 (2): 206--19.

\leavevmode\hypertarget{ref-cohen2008getting}{}%
Cohen, K Bretonnel, and Lawrence Hunter. 2008. {`Getting Started in Text
Mining.'} \emph{PLoS Computational Biology} 4 (1): e20.

\leavevmode\hypertarget{ref-dietterich2000ensemble}{}%
Dietterich, Thomas G. 2000. {`Ensemble Methods in Machine Learning.'} In
\emph{International Workshop on Multiple Classifier Systems}, 1--15.
Springer.
